Beam-Helicity and Beam-Charge Asymmetries\\ Associated with Deeply Virtual Compton Scattering\\ on the Unpolarised Proton \underline{Paper Tag: PDVCS0607 (v3.0)} \underline{Drafting Committee: DC90 (\today)}

### 2012-03-21 paper.tex
Made the changes requested by Gunar and Klaus post-submission to the DESY directorate.

The contribution to the uncertainties on the amplitude measurements
arising from background in the data from neutral meson
production is predominantly due to the failure to identify one of
  the two photons from the decay of these neutral mesons. \red{The
    $\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}$ amplitudes are corrected for
  inclfuences from semi-inclusive pion production and an uncertainty is
  assigned to the affected amplitudes. A further uncertainty is assigned to
  these amplitudes for the influence of photons produced in decays of
  exclusively produced pions.} The procedure for estimating the corresponding
uncertainty on the measured amplitude values is described in detail in
refs.~\cite{Air08,Air09}. Each measurement in the $-t$, $x_{\textrm{B}}$ and
  $Q^{2}$ projections has this uncertainty estimated at the
  centre of the relevant kinematic bin and included as part of the
  total systematic uncertainty. \red{No correction is applied or uncertainty
    assigned to the amplitudes for the
    $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}$ or $\mathcal{A}_{\textrm{C}}$
    asymmetries because influences from meson production are expected to
    vanish when considering the difference between beam charges.}

@@

Table~\ref{table_systematic_contributions_0607} shows, for each
physically-motivated amplitude extracted from the 2006-2007 data (in a
single, overall kinematic bin), the contribution of the various
systematic uncertainties. The beam polarisation measurements have total uncertainties of 2.8\% for the 1996-2005 data-taking period and 3.4\% for the 2006-2007 data taking period. These uncertainties are present in the beam-helicity amplitudes and are as independent scale uncertainties without inclusion in the other presented uncertainties.
\begin{table}
 \begin{center}
\resizebox{\textwidth}{!} {
 \begin{tabular}{|c|c||c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$& Background & Missing-Mass Shift  & Detector Effects & & Total $\delta_{syst.}$ \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  & 0.002 & 0.001 & 0.022 & & 0.022 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & 0.005  $\pm$  0.023  & 0.002 & 0.002 & 0.001 & & 0.003 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.023  & 0.003 & 0.001 & 0.001 & & 0.003 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.024 $\pm$  0.004 & 0.001 & 0.003 & 0.010 & & 0.011 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 & 0.002 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.004  $\pm$  0.005 & 0.001 & 0.000 & 0.014 & & 0.014 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.001  $\pm$   0.005 & 0.000 & 0.001 & 0.003 & & 0.004 \\
  \hline
 \end{tabular}
}
  \caption{The values of the physically-motivated asymmetries extracted in a single bin over all kinematic variables with their statistical uncertainties are presented in the second column of this table. The third, fourth and fifth columns show the contributions to the overall systematic uncertainties of the extracted asymmetry amplitudes due to the background correction, the time-dependent shifts of the missing-mass distributions and detector effects for the 2006-2007 data. The total
systematic uncertainties of the amplitudes, shown in the right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}
\section{Results}
In figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}, results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work are compared with results extracted from the 1996-2005\footnote{The hydrogen gas target for the data set of 1996-2005 was either unpolarised, transversely polarised or longitudinally polarised. However, the time-averaged polarisation of the polarised targets was negligible, while the rapid reversal time (60--180s) of the polarisation direction minimised bias due to detector effects.} data set published previously~\cite{Air09}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``Overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{bsa_sep}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the unpolarised 1996-2005 (open triangles)~\cite{Air09} and 2006-2007 (filled squares)
hydrogen data. The error bars represent the statistical uncertainties. The error bands represent the systematic uncertainties.
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the uncertainty of
the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}

@@

-0.036  $\pm$  0.074  $\pm$   0.007 & 0.069 $\pm$  0.071$ \pm$  0.013\\

@@

\bibitem{Bur00}
M.~Burkardt, \emph{Impact Parameter Dependent Parton Distributions and Off-Forward Parton Distributions for $\zeta\to 0$}
\\Phys. Rev. D \textbf{62} (2000) 071503 [ariv:hep-ph/0005108].
\\Erratum-ibid Phys. Rev. D \textbf{66} (2002) 119903.

>>>>

The contribution to the uncertainties on the amplitude measurements
arising from background in the data from neutral meson
production is predominantly due to the failure to identify one of
  the two photons from the decay of these neutral mesons. \red{The
    $\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}$ amplitudes are corrected for
  influences from semi-inclusive pion production and an uncertainty is
  assigned to the affected amplitudes. A further uncertainty is assigned to
  these amplitudes for the influence of photons produced in decays of
  exclusively produced pions.} The procedure for estimating the corresponding
uncertainty on the measured amplitude values is described in detail in
refs.~\cite{Air08,Air09}. Each measurement in the $-t$, $x_{\textrm{B}}$ and
  $Q^{2}$ projections has this uncertainty estimated at the
  centre of the relevant kinematic bin and included as part of the
  total systematic uncertainty. \red{No correction is applied or uncertainty
    assigned to the amplitudes for the
    $\mathcal{A}_{\textrm{LU}}^{\textrm{I}}$ or $\mathcal{A}_{\textrm{C}}$
    asymmetries because influences from meson production are expected to
    vanish when considering the difference between beam charges.}

@@

Table~\ref{table_systematic_contributions_0607} shows, for each
physically-motivated amplitude extracted from the 2006-2007 data (in a
single, overall kinematic bin), the contribution of the various
systematic uncertainties. The beam polarisation measurements have
total uncertainties of 2.8\% for the 1996-2005 data-taking period and
3.4\% for the 2006-2007 data taking period. These uncertainties are
present in the beam-helicity amplitudes and are\red{, as independent
  scale uncertainties, not included} in the other presented uncertainties.
\begin{table}
 \begin{center}
\resizebox{\textwidth}{!} {
 \begin{tabular}{|c|c||c|c|c|c|c|}
  \hline
 & $A$ $\pm$ $\delta_{stat.}$& Background & Missing-Mass Shift  & Detector Effects & & Total $\delta_{syst.}$ \\
  \hline
  \hline
  $A_{\textrm{LU,I}}^{\sin\phi}$ & -0.222  $\pm$  0.023  & 0.002 & 0.001 & 0.022 & & 0.022 \\
  \hline
  $A_{\textrm{LU,DVCS}}^{\sin\phi}$ & 0.005  $\pm$  0.023  & 0.002 & 0.002 & 0.001 & & 0.003 \\
  \hline
  $A_{\textrm{LU,I}}^{\sin(2\phi)}$ & 0.005  $\pm$  0.023  & 0.003 & 0.001 & 0.001 & & 0.003 \\
  \hline
  \hline
  $A_{\textrm{C}}^{\cos(0\phi)}$ & -0.024 $\pm$  0.004 & 0.001 & 0.003 & 0.010 & & 0.011 \\
  \hline
  $A_{\textrm{C}}^{\cos\phi}$ & 0.032  $\pm$  0.006 & 0.002 & 0.001 & 0.001 & & 0.002 \\
  \hline
  $A_{\textrm{C}}^{\cos(2\phi)}$ & -0.004  $\pm$  0.005 & 0.001 & 0.000 & 0.014 & & 0.014 \\
  \hline
  $A_{\textrm{C}}^{\cos(3\phi)}$ & 0.001  $\pm$   0.005 & 0.000 & 0.001 & 0.003 & & 0.004 \\
  \hline
 \end{tabular}
}
  \caption{The values of the physically-motivated asymmetries extracted in a single bin over all kinematic variables with their statistical uncertainties are presented in the second column of this table. The third, fourth and fifth columns show the contributions to the overall systematic uncertainties of the extracted asymmetry amplitudes due to the background correction, the time-dependent shifts of the missing-mass distributions and detector effects for the 2006-2007 data. The total
systematic uncertainties of the amplitudes, shown in the right-most column, are the individual contributions added in quadrature.}
  \label{table_systematic_contributions_0607}
\end{center}
\end{table}
\section{Results}
In figures~\ref{release_bsa_0607} and~\ref{release_bca_0607}, results for the beam-helicity and beam-charge asymmetry amplitudes extracted from the 2006-2007 hydrogen data sets in this work are compared with results extracted from the 1996-2005\footnote{The hydrogen gas target for the data set of 1996-2005 was either unpolarised, transversely polarised or longitudinally polarised. However, the time-averaged polarisation of the polarised targets was negligible, while the rapid reversal time (60--180s) of the polarisation direction minimised bias due to detector effects.} data set published previously~\cite{Air09}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``Overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{bsa_sep}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the unpolarised 1996-2005 (open triangles)~\cite{Air09} and 2006-2007 (filled squares)
hydrogen data. The error bars represent the statistical uncertainties. The error bands represent the systematic uncertainties.
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the uncertainty of
the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}

@@

-0.036  $\pm$  0.074  $\pm$ 0.007 & 0.069 $\pm$  0.071 $\pm$  0.013\\

@@

\bibitem{Bur00}
M.~Burkardt, \emph{Impact Parameter Dependent Parton Distributions and Off-Forward Parton Distributions for $\zeta\to 0$}
\\Phys. Rev. D \textbf{62} (2000) 071503 [arxiv:hep-ph/0005108].
\\Erratum-ibid Phys. Rev. D \textbf{66} (2002) 119903.
